Clean 2015 Raw Data

### 2018-11-04 data-raw/README.Rmd
Update data
Replaces FLD with PDL

devtools::use_data(RAW_data,
                   compress = "bzip2",
                   overwrite = TRUE)

devtools::use_data(AUDPS,
                   compress = "bzip2",
                   overwrite = TRUE)
```

@@

devtools::use_data(N_rates,
                   compress = "bzip2",
                   overwrite = TRUE)
```

>>>>

usethis::use_data(RAW_data,
                  compress = "bzip2",
                  overwrite = TRUE)

usethis::use_data(AUDPS,
                  compress = "bzip2",
                  overwrite = TRUE)
```

@@

usethis::use_data(N_rates,
                  compress = "bzip2",
                  overwrite = TRUE)
```
